### 2017-07-28 Paper01_EnthalpyAndCrystallization.tex
Results - Fragility - worked on writting and put in fits for both bulk and film

From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$. The temperature within the chamber was found to rise of $3 - 4$ \degree C, significantly less than the expected $20K$ suggested by similar set ups \cite{Wang2014}.

\acrshort{eds} analysis shows the nominal composition of bulk and film \MgZnCa~ is approximately the same.

@@

Relaxed \gls{dsc} of bulk material taken at different heating rates was used to establish the fragility of the \MgZnCa~ system. From the equations ... a fit of
$\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$ was established. This give a $D^{*}=20.4$ which using $D^{*}=590/(m-16)$ Shuai2014 [4, 5] gives a fragility $m=44.9$.

@@

>>>>

From the 35 minute depositions a nominal film thickness of $2.5 \mu m$ was obtained, giving a deposition rate of approximately $1.2 nm/s$. The temperature within the chamber was found to rise $3 - 4$\degree C, significantly less than the expected $20K$ suggested by similar setups \cite{Wang2014}.

\acrshort{eds} analysis shows good agreement in the nominal composition for both the bulk and film \MgZnCa, see Table \ref{tab:EDS_Composition}.

@@

@@

Variable heating rate \acrshort{dsc} for both the bulk and film \MgZnCa~ was used to establish the fragility of the system. Numerical solutions where used to fit the equation $\beta^{-1} = \tau_{0}~ e^{(\frac{D^{*}T_{0}}{T-T_{0}})}$ [source] for both the bulk and film. The fragility $m$ could then be calcuated from the relationship $D^{*}=590/(m-16)$ Shuai2014 [4, 5].

For the bulk it was found $\beta^{-1} = 1.338E - 16e^{5274 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.972$, giving a $D^{*}=20.4$, and a fragility $m=44.9$. For the film $\beta^{-1} = 5.921E - 11e^{2766 (\frac{1}{T-T_{0}})}$ with Adj. $R^{2}=0.861$, giving a $D^{*}=10.0$, and fragility $m=75.0$. See Figure \ref{fig:Fragility_BulkFilm_mValue}.
